opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-11-28 chapters/01_introduction.tex
Revised paragraph describing projected impact of opXRD database

The broad range of available experimental samples contained in the opXRD v1.0 database makes it possible to apply state-of-the-art ML approaches to the domain of powder XRD analysis. Sharing raw powder diffraction data is in the interest of 
We hope that this will yield more advanced automated ML approaches in the future, which can readily be applied in high-throughput experimentation pipelines.

>>>>

The broad range of available experimental samples contained in the opXRD v1.0 database makes it possible to apply state-of-the-art ML approaches to the domain of powder XRD analysis. We hope that this can drive ML research in this field towards more advanced automated analysis workflows that can accelerate material science research through ready application in high-throughput experimentation pipelines.
